### 2022-04-24 greta/sn_mcmc.Rmd
:broom:

```{r setup, message=FALSE}
library(tidyverse, quietly = TRUE)
library(greta, quietly = TRUE)
library(bayesplot, quietly = TRUE)
source("R/utils.R")
source("R/hopf.R")
```

@@

```{r}
pars = list(r = 1,
            K = 1,
            s = 0.1,
            h_init = .15,
            alpha = 0.0015,
            mu = 0,
            sigma = 0.02,
            t_init = 0
          )
t_max <- train_t_max + test_t_max

@@

```{r}
m <- greta_model_stoch(train)
bench::bench_time({                 
  draws <- mmcmc(m, n_samples = 60000, warmup = 50000,
                 chains = 4, verbose = FALSE)
})
```

>>>>

```{r setup, message=FALSE}
library(tidyverse, quietly = TRUE)
library(greta, quietly = TRUE)
library(bayesplot, quietly = TRUE)
source("R/utils.R")
source("R/saddle_node.R")
```

@@

```{r}
p <- list(r = 1,
          K = 1,
          s = 0.1,
          ho = .15,
          alpha = 0.0015,
          mu = 0,
          sigma = 0.02,
          t_init = 0,
          N_init = 0.75
        )
t_max <- train_t_max + test_t_max

@@

```{r}
m <- greta_model_sn(train)
bench::bench_time({                 
  draws <- mmcmc(m, n_samples = 60000, warmup = 50000,
                 chains = 4, verbose = FALSE)
})
```

### 2022-04-24 greta/stochastic_mcmc.Rmd
:broom:

```{r setup, message=FALSE}
library(tidyverse, quietly = TRUE)
library(greta, quietly = TRUE)
library(bayesplot, quietly = TRUE)
source("R/utils.R")
source("R/hopf.R")
```

>>>>

```{r setup, message=FALSE}
library(tidyverse, quietly = TRUE)
library(greta, quietly = TRUE)
library(bayesplot, quietly = TRUE)
source("R/utils.R")
source("R/stochastic.R")
```
